Two years of CiTO annotations

### 2022-08-26 article.Rmd
Started reporting/summarizing the Results

---
title: "Two years of CiTO annotations"
author:
- Egon Willighagen [1,*,orcid:0000-0001-7542-0286]
link-citations: yes
output:
  html_document:
    pandoc_args:
    - --lua-filter=filters/extract-cito.lua
    - --citeproc
    - --lua-filter=filters/insert-cito-in-ref.lua
  pdf_document:
    pandoc_args:
    - --lua-filter=filters/extract-cito.lua
    - --citeproc
    - --lua-filter=filters/insert-cito-in-ref.lua
  word_document:
    pandoc_args:
    - --lua-filter=filters/extract-cito.lua
    - --citeproc
    - --lua-filter=filters/insert-cito-in-ref.lua
# RStudio: cito-bibliography: bibliography.bib
# Other: bibliography: bibliography.bib
cito-bibliography: bibliography.bib
csl: journal-of-cheminformatics.csl
...

@@

XXXXX

>>>>

---
title: "Two years of CiTO annotations"
author:
- Egon Willighagen [1,*,orcid:0000-0001-7542-0286]
link-citations: yes
geometry: margin=2.5cm
output:
  html_document:
    pandoc_args:
    - --lua-filter=filters/extract-cito.lua
    - --citeproc
    - --lua-filter=filters/insert-cito-in-ref.lua
  pdf_document:
    pandoc_args:
    - --lua-filter=filters/extract-cito.lua
    - --citeproc
    - --lua-filter=filters/insert-cito-in-ref.lua
  word_document:
    pandoc_args:
    - --lua-filter=filters/extract-cito.lua
    - --citeproc
    - --lua-filter=filters/insert-cito-in-ref.lua
# RStudio: cito-bibliography: bibliography.bib
# Other: bibliography: bibliography.bib
cito-bibliography: bibliography.bib
csl: journal-of-cheminformatics.csl
...

@@

|**Year** |**Type**  |**Article** |**Intentions** | **% Annotated citaions** |
--- |----- |------------ |------------ |---
|Year 1|Editorial|Adoption of the Citation Typing Ontology by the *Journal of Cheminformatics* [@citesForInformation:Willighagen_2020]|cito:citesAsAuthority, cito:citesForInformation, cito:usesMethodIn||
||Methodology|Predicting target profiles with confidence as a service using docking scores [@citesForInformation:Ahmed2020]|cito:agreesWith, cito:extends, cito:citesAsAuthority, cito:citesAsDataSource, cito:usesMethodIn|
||Research article|Too sweet: cheminformatics for deglycosylation in natural products [@citesForInformation:Schaub2020]|cito:citeAsAuthority, cito:citesForInformation, cito:usesDataFrom, cito:usesMethodIn||
||Educational|A ligand-based computational drug repurposing pipeline using KNIME and Programmatic Data Access: case studies for rare diseases and COVID-19 [@citesForInformation:Tuerkova2020]|cito:agreesWith, cito:citesAsAuthority, cito:citesAsDataSource, cito:discusses, cito:usesDataFrom, cito:usesMethodIn||
